SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-13 paper/pm-1-matrix.tex
fixed-dia

  \draw[->,thick] (n0) -- node[left=1mm]  {$0\overline{1}$} (n1);
  \draw [->,thick] (n0) to [bend right=-30] node[left=1mm]  {$\overline{01}23$} (n1);
  \draw [->,thick] (n1) to [bend right=-30] node[below=2pt,xshift=3pt]  {$01\overline{3}$} (n0);

@@

  \draw [->,thick] (n2) -- node[left=2pt]  {$2\overline{3}$} (n0);

>>>>

  \draw[->,thick] (n0) -- node[left=1mm]  {$0\overline{1}$} (n1);
  \draw [->,thick] (n0) to [bend right=-30] node[right=1mm]  {$\overline{01}23$} (n1);
  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$01\overline{3}$} (n0);

@@

  \draw [->,thick] (n2) -- node[right=2pt]  {$2\overline{3}$} (n0);
